Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-10-21 summary.Rmd
more simulations

* Number of vertices $n = 256, 512, 1024, 2048, 4096$
* Number of underlying communities $K = 2, 3, 4$
* Mixture parameters $\alpha_k = \frac{k^{-1}}{\sum_{l=1}^K l^{-1}}$ for 
$k = 1, ..., K$
* Community labels 
$z_k \stackrel{iid}{\sim} Multinomial(\alpha_K, ..., \alpha_K)$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

@@

## Replication and comparison of simulations from \citet*{307cbeb9b1be48299388437423d94bf1}

```{r clust_err_sc, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against modularity maximization (blue) for sample size equal to 400. Simulations were repeated 50 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.height = 2, fig.width = 6}
clustering.mm.df <- readr::read_csv('clustering-sim-sc.csv')
clustering.ase.df <- readr::read_csv('clustering-sim-sc-ase.csv')
clustering.df <- dplyr::bind_rows(
  clustering.mm.df %>% 
    dplyr::transmute(method = 'Modularity maximization',
                     homophily = homophily,
                     error = pa.err),
  clustering.ase.df %>% 
    dplyr::transmute(method = 'Algorithm 2',
                     homophily = homophily,
                     error = pa.err)
)
clustering.df %>%
  dplyr::group_by(method, homophily) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  labs(y = 'community detection \nerror', 
       colour = NULL) +
  geom_line(aes(x = homophily, y = med.err, colour = method)) +
  geom_errorbar(aes(x = homophily, ymin = first.q, ymax = third.q,
                    colour = method)) + 
  scale_colour_brewer(palette = 'Set1') + 
  # coord_fixed(1) + 
  scale_y_log10()
```

@@

zhat.dblp <- cluster.pabm(A.dblp, 2, use.all = TRUE, normalize = FALSE)
dblp.acc <- mean(zhat.dblp == z.dblp)
dblp.acc <- ifelse(dblp.acc < .5, 1 - dblp.acc, dblp.acc)
```

@@

```{r}
dplyr::tibble(network = c('British MPs', 'Political blogs', 'DBLP'),
              vertices = c(nrow(A.bmp), nrow(A.pb), nrow(A.dblp)),
              `error (modularity maximization)` = c(round(1 / 329, 3),
                                                    round(61 / 1222, 3),
                                                    round(62 / 2203, 3)),
              `error (algorithm 2)` = round(1 - c(bmp.acc, 
                                                  pb.acc,
                                                  dblp.acc), 3)) %>% 
  knitr::kable(caption = paste('Community detection error rates', 
                               'for modularity maximization',
                               '(\\citet{307cbeb9b1be48299388437423d94bf1})',
                               'and Algorithm 2.'))
```

>>>>

* Number of vertices $n = 256, 512, 1024, 2048, 4096$
* Number of underlying communities $K = 2, 3, 4$
* Mixture parameters $\alpha_k = \frac{k^{-1}}{\sum_{l=1}^K l^{-1}}$ for 
$k = 1, ..., K$
* Community labels 
$z_k \stackrel{iid}{\sim} Multinomial(\alpha_1, ..., \alpha_K)$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

@@

@@

zhat.dblp <- cluster.pabm(A.dblp, 2, use.all = TRUE, normalize = FALSE)
dblp.acc <- mean(zhat.dblp == z.dblp)
dblp.acc <- ifelse(dblp.acc < .5, 1 - dblp.acc, dblp.acc)

zhat.bmp.ssc <- ssc(A.bmp, 2, 1e-3)
bmp.acc.ssc <- mean(zhat.bmp.ssc == z.bmp)
bmp.acc.ssc <- ifelse(bmp.acc.ssc < .5, 1 - bmp.acc.ssc, bmp.acc.ssc)

zhat.pb.ssc <- ssc(A.pb, 2, 1e-4)
pb.acc.ssc <- mean(zhat.pb.ssc == z.pb)
pb.acc.ssc <- ifelse(pb.acc.ssc < .5, 1 - pb.acc.ssc, pb.acc.ssc)

zhat.dblp.ssc <- ssc(A.dblp, 2, 1e-2)
dblp.acc.ssc <- mean(zhat.dblp.ssc == z.dblp)
dblp.acc.ssc <- ifelse(dblp.acc.ssc < .5, 1 - dblp.acc.ssc, dblp.acc.ssc)
```

@@

```{r}
dplyr::tibble(network = c('British MPs', 'Political blogs', 'DBLP'),
              vertices = c(nrow(A.bmp), nrow(A.pb), nrow(A.dblp)),
              `error (mod. max.)` = c(round(1 / 329, 3),
                                      round(61 / 1222, 3),
                                      round(62 / 2203, 3)),
              `error (SSC)` = round(1 - c(bmp.acc.ssc,
                                          pb.acc.ssc,
                                          dblp.acc.ssc), 3),
              `error (alg. 2)` = round(1 - c(bmp.acc, 
                                                  pb.acc,
                                                  dblp.acc), 3)) %>% 
  knitr::kable(caption = paste('Community detection error rates', 
                               'for modularity maximization,',
                               'sparse subspace clustering, ',
                               'and Algorithm 2.'))
```
